### 2024-08-29 actuarial.qmd
20240829 - steps to conduct actuarial approaches

>>>>

## Steps to Conduct Actuarial Approaches {#sec-stepsActuarial}

Here are several steps to conduct actuarial approaches [@DenHartigh2018; @Kahneman2011]:

1. Determine a set of relevant variables to measure
1. Determine how you will combine the variables
    - Do some variables have more weight than other variables?
1. Determine how the variables will be scored
    - e.g., a 7-point likert scale
1. Combine the scores based on the pre-specified formula
1. Use the final score to make your prediction (for selecting players)
